Untitled

### 2019-05-28 manuscript/manuscript draft.Rmd
updated manuscript draft

*Model specification.* The effects of climate and latitude on primary productivity were analysed using mixed effects models using the package 'lme4' in R v. 1.1.463 (cite).

>>>>

*Model specification.* The effects of climate and latitude on primary productivity were analysed using mixed effects models using the package 'lme4' in R v. 1.1.463 (cite). The effect of each extracted climate variable on each measure of primary productivity was modelled by specifying the climate variable as a fixed effect. Site altitude was also included as a fixed effect. Random effect was stand nested within area. Data from the temperate regions was heavily skewed towards studies from the old-growth forests of the Pacific Northwest. These forests have very high productivity, and so to reduce any bias from over-sampling of this region, the models were weighted according to the proportion of forest cover by Koeppen climate zone.
